---
title: "Comparing Suicide Rates"
author: "<center><div class='mysubtitle'>See the code on [github](https://github.com/Barnes7599/suicide_rates).</div></center>"
output:
  html_document:
    css: style.css
    theme: yeti
    code_folding: hide
    includes:
      before_body: header.html
      after_body: footer.html
---

<div class="mycontent">

<center>
<!-- ![]() -->
Photo by <a href="https://unsplash.com/@kalvisuals?utm_source=unsplash&utm_medium=referral&utm_content=creditCopyText">KAL VISUALS</a> on <a href="https://unsplash.com/s/photos/lanscape?utm_source=unsplash&utm_medium=referral&utm_content=creditCopyText">Unsplash</a>
  
<br>
Disclaimer: This project is not affiliated, associated, authorized, endorsed by, or in any way officially connected with Our World in Data, or any of its subsidiaries or its affiliates. The official Our World in Data website can be found [here](https://ourworldindata.org/)
</center> 
<br><br>

---

Give narrative of project

Lets get started

```{r setup, include=FALSE}

knitr::opts_chunk$set(
  echo = FALSE,
  message = FALSE,
  warning = FALSE,
  cache = TRUE,
  fig.align = "center",
  tidy = "formatR"
)
options(scipen = 999) # keep scientific notation turned off
unlink("index.cache", recursive = TRUE)

```

<h3> **Load Libraries** </h3>

Load packages - you may need to install packages using the install.packages() function. Make sure you put the package name in quotes like install.packages("tidyverse"), you will only have to do this once. 

```{r, echo = TRUE}
library(tidyverse)
library(lubridate)
library(readxl)
library(showtext)
library(ggtext)
library(glue)
library(patchwork)
library(highcharter)
```

---

<h3> **Load the data** </h3>

Data set is located at:[Dataset](https://ourworldindata.org/suicide#) <br>
Dataset about page located here:[About]()

I typically use the [janitor](https://github.com/sfirke/janitor) package whenever I read in a data set. it cleans up the column headings by making them all lower case and placing an underscore between spaces. 

```{r, echo= TRUE}


```




