---
title: "<center><div class='mytitle'>Comparing Suicide Rates from 1990 to 2019</div></center>"
author: "<center><div class='mysubtitle'>See the code on [github](https://github.com/Barnes7599/suicide_rates).</div></center>"
output:
  html_document:
    css: style.css
    theme: "yeti"
    code_folding: hide
    includes:
      before_body: header.html
      after_body: footer.html
---

<div class="mycontent">

<center>
![]()
<br>
<!-- Disclaimer: This project is not affiliated, associated, authorized, endorsed by, or in any way officially connected with DC 311, or any of its subsidiaries or its affiliates. The official DC 311 website can be found [here](https://311.dc.gov/citizen/home) -->
</center> 
<br><br>

---

Give narrative of project

Lets get started

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  echo = FALSE,
  message = FALSE,
  warning = FALSE,
  cache = TRUE,
  fig.align = "center",
  tidy = "formatR"
)
options(scipen = 999) # keep scientific notation turned off
unlink("index.cache", recursive = TRUE)

```

<h3> **Load Libraries** </h3>

Load packages - you may need to install packages using the install.packages() function. Make sure you put the package name in quotes like install.packages("tidyverse"), you will only have to do this once. 

```{r, echo = TRUE}
library(tidyverse)
library(lubridate)
library(readxl)
library(showtext)
library(ggtext)
library(glue)
library(patchwork)
library(highcharter)
```

---
<h3> **Load the data** </h3>

Data set is located at:[Dataset](https://ourworldindata.org/suicide#) <br>
Dataset about page located here:[About](https://opendata.dc.gov/datasets/DCGIS::311-city-service-requests-in-2022/about)

I typically use the [janitor](https://github.com/sfirke/janitor) package whenever I read in a data set. it cleans up the column headings by making them all lower case and placing an underscore between spaces. 

```{r, echo= TRUE}

service_calls_2022 <- read_csv("https://raw.githubusercontent.com/Barnes7599/DCServiceRequests311/main/DC_service_calls.csv") %>%
  janitor::clean_names()
```



---


